---
title: "Reproducible Research: Peer Assessment 1"
date: "5/30/2021"
output: html_document
---

## Setting Global Option

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading and processing data

```{r loadingdata}
unzip("activity.zip")
activity <- read.csv("activity.csv")
activity$date <- as.Date(activity$date, "%Y-%m-%d")
```
## What is mean total number of steps taken per day?

**Histogram of the total number of steps taken each day**
```{r stepsperday}
library(dplyr)
library(ggplot2)

act_bydate <- group_by(activity, date)
stepsperday <- summarize(act_bydate, steps=sum(steps, na.rm=TRUE))

g <- ggplot(stepsperday, aes(date, steps))
g+geom_col(color="black", fill="blue")+labs(title="Total Steps Taken Each Day")

stepsmean <- mean(stepsperday$steps)
stepsmedian <- median(stepsperday$steps)
```

**Mean of the total number of steps taken per day is: `r stepsmean`**  
**Median of the total number of steps taken per day is: `r stepsmedian`**

## What is the average daily activity pattern?

```{r stepsbyinterval}
act_byinterval <- group_by(activity, interval)
steps_interval<- summarize(act_byinterval, steps=mean(steps, na.rm=TRUE))
with(steps_interval, plot(interval, steps, type="l"))
mtext("Average number of steps taken in each 5-minute interval")
max_steps <- max(steps_interval$steps)
max_interval <- steps_interval[steps_interval$steps>=max_steps, 1]
```
**On average across all the days in the dataset, interval `r max_interval` contains the maximum number of steps of `r max_steps`**


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
